A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-09-30 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
moved figure of steady state results

The model primarily converges to steady state due to factors such as
signature request frequency, node availability, group creation/expiration, and....

\textit{ Steady state active group count:} Groups are generated with every request, and intially
during the bootstrap phase a set number of groups are generated with available nodes. In the current
simulation, requests are generated as coin toss at each step. The steady state number of active groups
is a function of number of new requests and rate of group expiry. Initially we

@@

\newpage

\begin{figure*}[h]
    \onecolumn
    \centering
    \includegraphics[width=\linewidth]{steady_state_behavior.pdf}
    \caption{Emergence of Steady State Behavior}
    \label{fig:steady_state}
\end{figure*}

\newpage
\bibliographystyle{plain}
\bibliography{Simulation_paper.bib}
\end{document}

>>>>

The model primarily converges to steady state due to factors such as
signature request frequency, node availability, and group creation/expiration. We discuss a few
steady state values of interest.

\textit{Active group count} Groups are generated with every request, and intially
during the bootstrap phase a set number of groups are generated with available nodes. In the current
simulation, requests are generated as coin tosses (binomial) at each step. The steady state number of 
active groups is a function of number of new requests and rate of group expiry. In the current setup, 
we see the number of active groups converging to 15 after 400 blocks.

@@

\bibliographystyle{plain}
\bibliography{Simulation_paper.bib}

\begin{figure*}[h]
    \onecolumn
    \centering
    \includegraphics[width=\linewidth]{steady_state_behavior.pdf}
    \caption{Emergence of Steady State Behavior}
    \label{fig:steady_state}
    \multicolumn
\end{figure*}

\end{document}
